\documentclass{article}

\usepackage[margin=1.2in]{geometry}
\usepackage[utf8]{inputenc}

\setlength{\parindent}{0cm}

%\firstname{Bardia}
%\familyname{Zamani Abnili}
%\email{BarZamSr@gmail.com}

\begin{document}

\hrulefill

\begin{itemize}
	\item Australian Citizen
	\item Full rights to work in Australia
	\item Fully vaccinated against Covid-19
\end{itemize}

\hrulefill

Recent graduate with a year of internship experience, seeking to start a career in data science.
\bigskip\\
Graduated with a Bachelors of Science from the University of Melbourne in July of 2022, majoring in Computing and Software Systems.
\bigskip\\
Interned for a year with the Digital Twin (DT) research team in CSDILA, and delivered several pieces of software complete with testing and documentation.
\bigskip\\
Detail-oriented analytical thinker, and a creative problem solver.

\hrulefill

\section*{Skills Summary}
\subsection*{Technical}
\begin{itemize}
	\item Experienced in a variety of programming languages (including Python, Java, C, C++, Javascript, Hascal, and R).
	\item Knowledgable in programming paradigms and techniques, including object oriented programming (OOP) patterns and principles, functional programming, debugging, and test-driven development (TDD).
	\item Experienced in Agile/SCRUM methodologies and its associated tools (Jira, Confluence, Trello, BitBucket).
	\item Experienced with working via command line interface (CLI), zsh, bash, and writing shell scripts.
	\item Experienced in several data processing, 3D modelling and multi-threading libraries for Python (such as Numpy, Pandas, PyTorch, IFCOpenShell, Multiprocessing and TriMesh).
	\item Experienced with geospatial technologies such as Cesium, 3DTiles, Industry Foundation Classes (IFC), Building Information Models (BIM).
	\item Familiar with data science, processing and analysis, such as data cleaning and modelling, and dimensionality reduction.
	\item Familiar with many machine learning techniques and methods, including gradient descent, backward propagation, evolutionary algorithms, neural networks, deep neural networks and generative adversarial networks (GANs)).
	\item Familiar with relational database management (indexing, optimisation, etc.) and Structured Query Language (SQL).
	\item Experienced with various software suites such as MatLab, the Microsoft Office suite (Word, Excel, PowerPoint).
\end{itemize}

\subsection*{Inter-personal}
\begin{itemize}
	\item Able to assess and analyse interactions and relationships and gauge the chemistry of a team.
	\item Skilled and experienced in conflict-resolution and reaching satisfactory compromises.
	\item Excellent verbal and written communication skills.
\end{itemize}

\end{document}
